The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2023-11-29 src/paper/theory.tex
Finish example application

>>>>

\subsection{Comparison}

Let us now compare the outcomes at the three cases by looking at the entry fees for side $i$.
From the previous results, they are
\begin{align*}
    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
    p_i^b &= \underbracket{\frac{\lambda_i}{\lambda_P + \lambda_i} F_i}_{(1)} - \underbracket{\frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} \\
    &+ \underbracket{\frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} +
    - \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds}_{(4)},
\end{align*}
for the welfare-maximizing, unilateral price setting and bargaining cases, respectively.

All of these expressions bear some similarities to each other, in that the price is somehow related to the externalities that an entrant imposes on the other players.
In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
The unilateral pricing case also includes these two factors in full, but also adds a third factor, related to the elasticity of entry (3).
Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it can extract depends on $\phi'_i(u_i)$ (or, equivalently, $\kappa'_i(u_i)$).
It is the same mechanism that leads to the markup in the simple monopolistic pricing model.

The bargaining case also has the first two factors, albeit they are somewhat different.
As opposed to the first two cases, the price only contains some fraction of the externalities, and the rest is shared with the platform and the other side.
Furthermore, some part of the welfare generated on side $i$ is also shared with the other players, and thus appears in the price (4).
Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.

Whether these departures lead to a higher or lower total welfare depends on the specific parameters of the model.
For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to lower entry and total surplus than not only the welfare-maximizing case, but also the unilateral pricing case.
That is, everybody looses from bargaining.\footnote{
    In such a case, the platform would like to set lower entry fees that what it can achieve via bargaining.
    While in some settings it is very plausible that it can do it, in others commitment problems might prevent it from doing so.
}

On the other hand, if $\lambda_P$ is sufficiently low, then one can find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining.
The total welfare is also between the welfare-maximizing and unilateral pricing cases, therefore bargaining can be beneficial as an alternative of unilateral pricing.
The platform, however, achieves a lower profit than if it could set the entry fees unilaterally.

Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.\footnote{
    Given that $\alpha_i > 0, i \in \{1, 2\}$.
}
The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
This also implies that the total welfare is strictly lower than in the welfare-maximizing case.
Therefore, while bargaining can be welfare-increasing compared to unilateral price setting, it can not achieve the maximum possible welfare.\footnote{
    One could argue that the welfare maximizing case is not a realistic benchmark anyway, as it assumes that the platform is making a loss.
}
